
\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=1.4cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{array}

\definecolor{linkcol}{RGB}{0,0,0}
\hypersetup{
  colorlinks=true,
  urlcolor=linkcol,
  linkcolor=linkcol
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Section styling (similar to screenshot: small caps + rule)
\titleformat{\section}
  {\scshape\large\raggedright}
  {}{0pt}{}[\vspace{-4pt}\titlerule\vspace{4pt}]
\titlespacing*{\section}{0pt}{10pt}{6pt}

% Lists
\setlist[itemize]{leftmargin=*, topsep=0.5pt, itemsep=0.5pt, parsep=0pt, partopsep=0pt}

% Helpers
\newcommand{\cvname}[1]{\textbf{\LARGE #1}}
\newcommand{\cvmeta}[1]{\small #1}
\newcommand{\cventry}[4]{%
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
    #3 & \textit{#4} \\
  \end{tabular*}\vspace{2pt}
}
\newcommand{\cventryone}[3]{%
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
    #3 & \\
  \end{tabular*}\vspace{2pt}
}
\newcommand{\cvsubheading}[4]{%
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & \textit{#2} \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{2pt}
}
\newcommand{\cvproject}[2]{\textbf{#1} \hfill \textit{#2}\vspace{2pt}}
\newcommand{\smallgap}{\vspace{1.0pt}}

\begin{document}

% ===== Header =====
\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \cvname{Faran Zafar} & \cvmeta{\href{mailto:faranzafarcs@gmail.com}{faranzafarcs@gmail.com}} \\
  \cvmeta{Birmingham, UK \;|\; (+44) 7355-889332 \;|\; \href{https://faranz.com}{faranz.com}} & \cvmeta{} \\
\end{tabular*}
\vspace{2pt}

% ===== Experience =====
\section{Experience}


\cventry{Founder \& CTO}{2025 -- Present}{Ovalens (\href{https://ovalens.com}{ovalens.com}), London, UK}{}
\begin{itemize}
  \item Raised \pounds7k through a hackathon win.
  \item Implemented a deterministic UK tax engine (16 modules) incl. income tax (ENG/SCO), NI, AA, HICBC, loans, ANI, BED/ISA.
  \item Shipped Claude-powered chat (streaming) with 6 tools for modelling, dashboards, and note search.
  \item Delivered 30+ REST APIs, async processing via Redis, 280+ tests, and production observability with Sentry + metrics.
\end{itemize}
\smallgap

\cventry{Software Engineer}{Dec 2024 -- Present}{RealityMine, Manchester, UK}{}
\begin{itemize}
  \item Built production backend automation for critical server diagnostics, cutting MTTR from \(\sim\)60 minutes to minutes (estimated \(\sim\)\pounds500k in manual hours).
  \item Built customer-facing configuration workflows, saving \(\sim\)350+ hours/year through reliable end-to-end automation.
  \item Optimized a \(\sim\)600GB/day data pipeline, improving throughput by \(\sim\)86\%.
  \item Reduced legacy system alarms/crashes by \(\sim\)95\% through reliability improvements.
\end{itemize}
\smallgap

\cventry{Research Intern}{Jul 2024 -- Aug 2024}{Google DeepMind, Birmingham, UK}{}
\begin{itemize}
  \item Co-developed the Adaptive Memory RAG (AMRAG) framework integrating self-checks and web search, improving response accuracy by 88\%.
  \item Applied decomposition, QA context generation, hallucination detection, and retrieval augmentation.
  \item Achieved sub-5-second response times, outperforming standard RAG baselines.
\end{itemize}
\smallgap

\cventry{Teaching Assistant (College of Engineering and Physical Sciences)}{Oct 2023 -- Jul 2024}{Aston University, Birmingham, UK}{}
\begin{itemize}
  \item Mentored 10+ student teams (6 members each) in OOP, emphasizing best practices.
  \item Led 8+ hands-on workshops on advanced OOP topics (30--50 students per session).
\end{itemize}

% ===== Education =====
\section{Education}

\cventryone{Aston University, Birmingham, UK}{Sep 2021 -- Sep 2024}{BSc Computer Science \;\textit{(First Class Honours, 4.0 GPA)}}%

% ===== Skills =====
\section{Skills \& Certifications}

\textbf{GenAI:} AWS Bedrock, LangChain/LangGraph, LlamaIndex, tool calling, structured outputs, prompt-injection mitigation, RAG, Pinecone, pgvector \\
\textbf{Stack:} FastAPI, Django, Flask, Spring Boot; React, Next.js \\
\textbf{Infra/Data:} AWS, Docker, Linux, CI/CD pipelines; PostgreSQL, MySQL, MongoDB; Firebase, Redis, RabbitMQ \\
\textbf{Languages/Certs:} Python, Java, JavaScript, C\#, PHP, C++; Google Cybersecurity Certificate; AWS Solutions Architect (in progress)

% ===== Projects =====
\section{Projects}


\cvproject{\href{https://heyitsdonald.com}{Donald (heyitsdonald.com)}}{}
\begin{itemize}
  \item Full-stack voice CV coach: Claude tool-only analysis, ElevenLabs, Firecrawl research; FastAPI, Next.js, PostgreSQL, Redis, and Celery-backed workers with rate limits for long voice sessions.
  \item Launch traction: \(\sim\)40k views in 72 hours, 300+ users, and \$4.1M+ in modeled tuition impact.
\end{itemize}
\smallgap

\cvproject{GetOut}{}
\begin{itemize}
  \item Conversational ``social wingman'' (voice/text): Next.js~14 + Cloudflare Worker; D1, Vectorize embeddings, 3 Durable Objects, 2 Queues, Workers AI.
  \item Tool-calling agent (5 tools, 3 event plugins), OAuth/JWT/Firebase + webhook routes, Sentry; ElevenLabs; LLM-as-judge eval (Llama~3.1~8B) to D1.
\end{itemize}
\smallgap

\cvproject{Katsu}{}
\begin{itemize}
  \item Built a production operations platform cutting MTTR from 1--2 hours to minutes with automated verification and workflow orchestration.
  \item Implemented secure multi-agent remediation (prompt-injection defense, SSH session pooling) and optimized runtime to \(\sim\)\$0.02/request for always-on alarm resolution.
\end{itemize}
\smallgap

\cvproject{Flashbits \,(Sold)}{}
\begin{itemize}
  \item Swipe-based mobile interview prep app with AI-generated quizzes, spaced repetition, and a recommendation engine across 14 DSA topic categories.
  \item Gamified XP/ranks, analytics dashboard, and company-specific filtering; shipped 1{,}700+ curated MCQ-style problems.
\end{itemize}
\smallgap



\vfill
\cvmeta{More projects at \href{https://faranz.com}{faranz.com}; Donald at \href{https://heyitsdonald.com}{heyitsdonald.com}; Ovalens at \href{https://ovalens.com}{ovalens.com}.}

\end{document}
